\section{Introduction}

The present user manually describes the entire image processing pipeline for 2D crystals in {\twodx}. For more detailed background information we refer to \cite{marheit1, marheit2, marheit3}.

The latest version of the manual is available on \url{http://www.2dx.unibas.ch/documentation/2dx-software/2dx-user-manual-.pdf}.

\subsection{What is {\twodx}?}

{\twodx} \cite{2dx_1, 2dx_2} is an initiative that aims at facilitating computer image processing in electron crystallography. Electron crystallography is our method of choice for the determination of the high-resolution structure of membrane proteins in the membrane-embedded state. This is done by recording cryo-electron microscopy images of two-dimensional membrane crystals of the membrane proteins, and reconstructing the 3D structure of the proteins by computer image processing of a larger number of images. 

We have created a software package called 2dx that aims at providing the user with user-guidance and help, and features streamlined processing solutions with optional full automation. The website \url{www.2dx.org} is the home of the 2dx software, and hosts the software itself, including the open source code, as well as the manual, that the users can annotate in blog form. 
2dx utilizes the excellent MRC software that was developed and is maintained at the MRC by R. Henderson and others\footnote{\url{http://www2.mrc-lmb.cam.ac.uk}}. While the latest edition of the original MRC software can be requested from Judith Short\footnote{JMS@mrc-lmb.cam.ac.uk}, we provide here on this 2dx.org server a slightly adapted version of the MRC software code in order to interface it with the 2dx system, and we also have added programs for automation and other functions. 

{\twodx} is also a repository for user experience and other software solutions. We provide a manual for the MRC software\footnote{\url{http://www.2dx.unibas.ch/documentation/mrc-software}}, which was contributed by Vinzenz Unger\footnote{\url{http://pantheon.yale.edu/~mfr28/members.htm}} and Anchi Cheng\footnote{\url{http://www.scripps.edu/~acheng/}}. We here also collect links and information about other software systems.

