\section{Single Particle Processing for 2D crystals}

In this section we provide detailed instruction on the single-particle refinement module integrated in 2dx since version 3.5.0. Detailed algorithmic background can be found in \cite{scherer2013single}.

In cases where ultra-flat cryo-preparations of well-ordered two-dimensional (2D) crystals are available, electron crystallography is a powerful method for the determination of the high-resolution structures of membrane and soluble proteins. However, crystal unbending and Fourier-filtering methods in electron crystallography three-dimensional (3D) image processing are generally limited in their performance for 2D crystals that are badly ordered or non-flat. Here we present a single particle image processing approach, which is implemented as an extension of the 2D crystallographic pipeline realized in the 2dx software package, for the determination of high-resolution 3D structures of membrane proteins. The algorithm presented, addresses the low single-to-noise ratio (SNR) of 2D crystal images by exploiting neighborhood correlation between adjacent proteins in the 2D crystal. Compared with conventional single particle processing for randomly oriented particles, the computational costs are greatly reduced due to the crystal-induced limited search space, which allows a much finer search space compared to classical single particle processing. To reduce the considerable computational costs, our software features a hybrid parallelization scheme for multi-CPU clusters and computer with high-end graphic processing units (GPUs).

\subsection{Create Container}
The first single-particle processing script \textit{"Create Container"} is used to create a folder storing all single-particle related files. Simply select/create a folder and run the script. Note that rerunning the script deletes the folder and sets up a new empty project folder.

\subsection{Generate Initial Model}

